### 2017-09-26 TF-vldb2018/sec-appendix.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\begin{widepage}
\vspace{-2ex}
\begin{center}
%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-diameter}
\includegraphics[scale=0.37]{./fig/youtube-semantic-diameter.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-density}
\includegraphics[scale=0.37]{./fig/youtube-semantic-density.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-capacity}
\includegraphics[scale=0.37]{./fig/youtube-semantic-capacity.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-link}
\includegraphics[scale=0.37]{./fig/youtube-semantic-link.eps}}
\vspace{-2.5ex}

%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-diameter-varyk}
\includegraphics[scale=0.37]{./fig/youtube-semantic-diameter-varyk.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-density-varyk}
\includegraphics[scale=0.37]{./fig/youtube-semantic-density-varyk.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-capacity-varyk}
\includegraphics[scale=0.37]{./fig/youtube-semantic-capacity-varyk.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-link-varyk}
\includegraphics[scale=0.37]{./fig/youtube-semantic-link-varyk.eps}}
\vspace{-2.0ex}

\end{center}
\vspace{-2.0ex}
\caption{Performance evaluation of \optgrouprec for top-$k$ team formation problem}
\label{exp-semantic-effectiveness-youtube}
%\end{widepage}
%\vspace{-0.5ex}
\end{figure*}

\begin{figure*}[tb!]
%\begin{widepage}
\vspace{-1.5ex}
\begin{center}
%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ (deletions)}]{\label{fig-exp-patinc-del-youtube}
\includegraphics[scale=0.395]{./fig/youtube-pattern-deletion.eps}}
\hspace{-1.7ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ (insertions)}]{\label{fig-exp-patinc-ins-youtube}
\includegraphics[scale=0.395]{./fig/youtube-pattern-insertion.eps}}
\hspace{-1.7ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ (capacity)}]{\label{fig-exp-patinc-cap-youtube}
\includegraphics[scale=0.395]{./fig/youtube-pattern-capchange.eps}}
\hspace{-1.7ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ (hybrid updates)}]{\label{fig-exp-patinc-hyb-youtube}
\includegraphics[scale=0.395]{./fig/youtube-pattern-hybrid.eps}}
\vspace{-2.5ex}

%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ (deletions)}]{\label{fig-exp-datainc-del-youtube}
\includegraphics[scale=0.395]{./fig/youtube-data-deletion.eps}}
\hspace{-1.7ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ (insertions)}]{\label{fig-exp-datainc-ins-youtube}
\includegraphics[scale=0.395]{./fig/youtube-data-insertion.eps}}
\hspace{-1.7ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ (hybrid updates)}]{\label{fig-exp-datainc-hyb-youtube}
\includegraphics[scale=0.395]{./fig/youtube-data-hybrid.eps}}
\hspace{-1.7ex}
\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ (simultaneous)}\hspace{-4.5ex}]{\label{fig-exp-hyb-patdata-youtube}
\includegraphics[scale=0.395]{./fig/youtube-pattern-data.eps}}
\vspace{-2.5ex}

%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ in update sets}]{\label{fig-exp-patinc-multi-youtube}
\includegraphics[scale=0.395]{./fig/youtube-pattern-multi.eps}}
%\hspace{-1.7ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ in update sets}]{\label{fig-exp-datainc-multi-youtube}
\includegraphics[scale=0.395]{./fig/youtube-data-multi.eps}}
%\hspace{-1.7ex}
\subfigure[{\scriptsize Varying $(|\Delta P|,|\Delta G|)$ in update sets}\hspace{-5.5ex}]{\label{fig-exp-hyb-datapat-multi-youtube}
\includegraphics[scale=0.395]{./fig/youtube-pattern-data-multi.eps}}
%\hfill
\vspace{-2.5ex}

\end{center}
\vspace{-2.0ex}
\caption{Performance evaluation of \inc for dynamic top-$k$ team formation problem (\youtube)}
\label{exp-inc-youtube}
%\end{widepage}
\vspace{-4ex}
\end{figure*}

@@

\vspace{-1.8ex}
\stitle{Exp-2: Efficiency of \inc for one set of updates}. Varying the amount of updates in one update set from 4.5\% to 45\% for pattern updates, 2.5\% to 25\% for data updates, and (4.5\%, 2.5\%) to (31.5\%, 17.5\%) for simultaneous updates, the results are reported in Fig.~\ref{fig-exp-patinc-del-youtube} to~\ref{fig-exp-hyb-patdata-youtube}.
We find \inc outperforms \optgrouprec when $\Delta P$, $\Delta G$ and $(\Delta P$, $\Delta G)$ are no more than 31.5\%, 20\% and (27\%, 15\%).
%for hybrid pattern, hybrid data, and simultaneous pattern and data updates.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\begin{widepage}
%\vspace{-2ex}
\begin{center}
%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-diameter}
\includegraphics[scale=0.38]{./fig/youtube-semantic-diameter.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-density}
\includegraphics[scale=0.38]{./fig/youtube-semantic-density.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-capacity}
\includegraphics[scale=0.38]{./fig/youtube-semantic-capacity.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-link}
\includegraphics[scale=0.38]{./fig/youtube-semantic-link.eps}}
\vspace{-2.5ex}

%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-diameter-varyk}
\includegraphics[scale=0.38]{./fig/youtube-semantic-diameter-varyk.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-density-varyk}
\includegraphics[scale=0.38]{./fig/youtube-semantic-density-varyk.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-capacity-varyk}
\includegraphics[scale=0.38]{./fig/youtube-semantic-capacity-varyk.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-link-varyk}
\includegraphics[scale=0.38]{./fig/youtube-semantic-link-varyk.eps}}
\vspace{-2.0ex}

\end{center}
\vspace{-3.0ex}
\caption{Performance evaluation of \optgrouprec for top-$k$ team formation problem}
\label{exp-semantic-effectiveness-youtube}
%\end{widepage}
%\vspace{-0.5ex}
\end{figure*}

\begin{figure*}[tb!]
%\begin{widepage}
%\vspace{-1.5ex}
\begin{center}
%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ (deletions)}]{\label{fig-exp-patinc-del-youtube}
\includegraphics[scale=0.38]{./fig/youtube-pattern-deletion.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ (insertions)}]{\label{fig-exp-patinc-ins-youtube}
\includegraphics[scale=0.38]{./fig/youtube-pattern-insertion.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ (capacity)}]{\label{fig-exp-patinc-cap-youtube}
\includegraphics[scale=0.38]{./fig/youtube-pattern-capchange.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ (hybrid updates)\hspace{-8.5ex}}]{\label{fig-exp-patinc-hyb-youtube}
\includegraphics[scale=0.38]{./fig/youtube-pattern-hybrid.eps}}
\vspace{-2.5ex}

%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ (deletions)}]{\label{fig-exp-datainc-del-youtube}
\includegraphics[scale=0.38]{./fig/youtube-data-deletion.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ (insertions)}]{\label{fig-exp-datainc-ins-youtube}
\includegraphics[scale=0.38]{./fig/youtube-data-insertion.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ (hybrid updates)}\hspace{-5.5ex}]{\label{fig-exp-datainc-hyb-youtube}
\includegraphics[scale=0.38]{./fig/youtube-data-hybrid.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ (simultaneous)}\hspace{-8.5ex}]{\label{fig-exp-hyb-patdata-youtube}
\includegraphics[scale=0.38]{./fig/youtube-pattern-data.eps}}
\vspace{-2.5ex}

%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ in update sets}]{\label{fig-exp-patinc-multi-youtube}
\includegraphics[scale=0.38]{./fig/youtube-pattern-multi.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ in update sets}]{\label{fig-exp-datainc-multi-youtube}
\includegraphics[scale=0.38]{./fig/youtube-data-multi.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ in update sets}\hspace{-8.5ex}]{\label{fig-exp-hyb-datapat-multi-youtube}
\includegraphics[scale=0.38]{./fig/youtube-pattern-data-multi.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Storage sizes}]{\label{fig-exp-extraspace}
\includegraphics[scale=0.38]{./fig/youtube-space.eps}}
\vspace{-2ex}

\end{center}
\vspace{-3.0ex}
\caption{Performance evaluation of \inc for dynamic top-$k$ team formation problem (\youtube)}
\label{exp-inc-youtube}
%\end{widepage}
\vspace{-3.0ex}
\end{figure*}

@@

\vspace{-1.8ex}
\stitle{Exp-2: Efficiency of \inc for one set of updates}. Varying the amount of updates in one update set from 4.5\% to 49.5\% for pattern updates, 2.5\% to 27.5\% (resp. 3\% to 33\%) for data insertions and hybrid data updates (resp. data deletions), and (4.5\%, 2.5\%) to (31.5\%, 17.5\%) for simultaneous pattern and data updates, the results are reported in Fig.~\ref{fig-exp-patinc-del-youtube} to~\ref{fig-exp-hyb-patdata-youtube}.
We find that \inc outperforms \optgrouprec when $\Delta P$, $\Delta G$ and $(\Delta P$, $\Delta G)$ are no more than 36\%, 22.5\% and (27\%, 15\%).
%for hybrid pattern, hybrid data, and simultaneous pattern and data updates.

### 2017-09-26 TF-vldb2018/sec-expt.tex

\subfigure[{\scriptsize Varying $|V_{P}|$ (\citationd)}]{\label{fig-exp-semantic-citation-diameter}
\includegraphics[scale=0.37]{./fig/citation-semantic-diameter.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\citationd)}]{\label{fig-exp-semantic-citation-density}
\includegraphics[scale=0.37]{./fig/citation-semantic-density.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\citationd)}]{\label{fig-exp-semantic-citation-capacity}
\includegraphics[scale=0.37]{./fig/citation-semantic-capacity.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\citationd)}]{\label{fig-exp-semantic-citation-link}
\includegraphics[scale=0.37]{./fig/citation-semantic-link.eps}}
\vspace{-2.5ex}

\subfigure[{\scriptsize Varying $k$ (\citationd)}]{\label{fig-exp-semantic-citation-diameter-varyk}
\includegraphics[scale=0.37]{./fig/citation-semantic-diameter-varyk.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $k$ (\citationd)}]{\label{fig-exp-semantic-citation-density-varyk}
\includegraphics[scale=0.37]{./fig/citation-semantic-density-varyk.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $k$ (\citationd)}]{\label{fig-exp-semantic-citation-capacity-varyk}
\includegraphics[scale=0.37]{./fig/citation-semantic-capacity-varyk.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $k$ (\citationd)}]{\label{fig-exp-semantic-citation-link-varyk}
\includegraphics[scale=0.37]{./fig/citation-semantic-link-varyk.eps}}
\vspace{-2.0ex}
\end{center}

@@

\stitle{Experimental Settings.} We use the following settings.

%\subsection{Experimental Settings}
%We used the following real-life and synthetic datasets.
\etitle{Data graphs.} We used a real-life and a synthetic dataset.

@@

@@

We used a PC with Intel Core i5-4570 CPU and 16GB of memory. We randomly generated 3 sets of input and repeated 5 times for each test. The average is reported here.
All the findings on \youtube are reported in the Appendix.

@@

\stitle{Exp-2: Effectiveness of \optgrouprec}.  We generated pattern graphs for \optgrouprec, and the corresponding queries (labels requirements) for \mindia, \minsumdis and \denalk, and manually checked the quality of matches returned by them. 
\looseness=-1

>>>>

\subfigure[{\scriptsize Varying $|V_{P}|$ (\citationd)}]{\label{fig-exp-semantic-citation-diameter}
\includegraphics[scale=0.38]{./fig/citation-semantic-diameter.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\citationd)}]{\label{fig-exp-semantic-citation-density}
\includegraphics[scale=0.38]{./fig/citation-semantic-density.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\citationd)}]{\label{fig-exp-semantic-citation-capacity}
\includegraphics[scale=0.38]{./fig/citation-semantic-capacity.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\citationd)}]{\label{fig-exp-semantic-citation-link}
\includegraphics[scale=0.38]{./fig/citation-semantic-link.eps}}
\vspace{-2.5ex}

\subfigure[{\scriptsize Varying $k$ (\citationd)}]{\label{fig-exp-semantic-citation-diameter-varyk}
\includegraphics[scale=0.38]{./fig/citation-semantic-diameter-varyk.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $k$ (\citationd)}]{\label{fig-exp-semantic-citation-density-varyk}
\includegraphics[scale=0.38]{./fig/citation-semantic-density-varyk.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $k$ (\citationd)}]{\label{fig-exp-semantic-citation-capacity-varyk}
\includegraphics[scale=0.38]{./fig/citation-semantic-capacity-varyk.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $k$ (\citationd)}]{\label{fig-exp-semantic-citation-link-varyk}
\includegraphics[scale=0.38]{./fig/citation-semantic-link-varyk.eps}}
\vspace{-2.0ex}
\end{center}

@@

\vspace{-0.2ex}
\stitle{Experimental Settings.} We use the following settings.

%\subsection{Experimental Settings}
%We used the following real-life and synthetic datasets.
\vspace{-0.3ex}
\etitle{Data graphs.} We used two real-life and a synthetic dataset.

@@

\ni (3) We also used real-life data \youtube~\cite{youtubeWeb} (see Appendix).

@@

We used a PC with Intel Core i5-4570 CPU and 16GB of memory. We randomly generated 3 sets of input and repeated 5 times for each test. The average is reported here.
%We also used another real-life dataset \youtube, which will be reported in the Appendix.

@@

\stitle{Exp-2: Effectiveness of \optgrouprec}.  We generated pattern graphs for \optgrouprec, and the corresponding queries (labels requirements) for \mindia, \minsumdis and \denalk, and checked the quality of matches returned by them. 
\looseness=-1
